---
title: "First Knit"
author: "Brandy Tovar"
date: "August 19, 2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?

###my answer  


I am sitting at the middle of the class. I am usually in the middle because it helps me fous.I am on computer 26. I dont like periodic seat re-assignments. I rate it at a 6  on a 1-10 scale with 10 being dislike very much. Yes, I have worked in teams and I found that it helps me get better grades.
  
   
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 


###my answer     
  
 
I would like to be called Brandy.



##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  
   
 I would like to become a registered nurse. I find that science courses are my greatest interests. I am currently trying to achieve my associates degree in nursing.




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  
   
I have been to Sweden in 2014, but I would like to visit Greece one day. I have not been in the military, but if I got drafted, I would enter the Air Force or Army because I am not a good swimmer so I would not make it in the Navy and I would not dare think to go to the Marines. 



##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?

 

###my answer     
  
   
I need to obtain a C, but I am aiming to attain an A or B. 


##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  
  I would rate my computer skills at a level 6. I do have have a google computer at home with internet access. 
  My means of transportaion is my car. I do not currently have issues that would limit when I can be in college. I atteneded Antelope Valley High School and graduated in 2011. Yes, I do currently have a full time job. 
  




